%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Rishi Shah
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style
\usepackage{amssymb}
\renewcommand{\labelitemi}{$\blacktriangleright$}
\usepackage[left=0.75in,top=0.4in,right=0.75in,bottom=0.6in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.1\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}

\name{Kuangzheng Li} % Your name
\address{\Large{(773)7861776 \ lik15@rpi.edu}}
%\address{1520 6th Street, Troy, NY 12180} % Your address
%\address{123 Pleasant Lane \\ City, State 12345} % Your secondary addess (optional)
 % Your phone number and email

\begin{document}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%-------------------------------------------------------------------------------https://www.overleaf.com/project/5da22db85d299400017d22cd---------

\begin{rSection}{Education}

{\bf Rensselaer Polytechnic Institute, Troy, NY} \hfill {\em August 2019 - December 2020}
\\ Master of Science in Information Technology

{\bf University of Science \& Technology of China, Hefei, China} \hfill {\em June 2016}
\\ Master of Science in Mathematics
\\ { Overall GPA: 3.6}

{\bf Ocean University of China, Qingdao, China} \hfill {\em June 2014}
\\ Bachelor of Science in Mathematics
\\ { Overall GPA: 3.5}
%Minor in Linguistics \smallskip \\
%Member of Eta Kappa Nu \\
%Member of Upsilon Pi Epsilon \\
\end{rSection}

%--------------------------------------------------------------------------------
%    Projects And Seminars
%-----------------------------------------------------------------------------------------------

\begin{rSection}{Professional Experience}
{\bf SweetCode Inc, Beijing, China} \hfill {\em March 2017 - August 2019}
\\ {\em  {Data Analyst}}
\begin{itemize}
\setlength{\topsep}{-0.1in}
\setlength{\itemindent}{-0.1in}
\setlength{\parskip}{0.5pt}

    \item {\bf Algorithm Designing for the Chinese Poker}\hfill{\em December 2017 - August 2019}
    \begin{itemize}
    \setlength{\parskip}{0.3pt}
        \item[\textbf{+}] Designed New Search algorithm(FPMCTS) for Chinese poker to address view switching and strategy fusion problems.
        \item[\textbf{+}] Lifted the artificial intelligence agent to be the strongest Chinese Poker AI with machine learning, including neural Network and bayesian method.
        \item[\textbf{+}] Built evaluation platform to identify performance and issues of the self-improve AI during training process with TrueSkill and data visualization.
    \end{itemize}

    \item {\bf Data Analytics for the Application of Chinese Poker}\hfill{\em November 2017 - May 2019}
    \begin{itemize}
        \item[\textbf{+}]
        Increased the number of games each player enrolled in the poker application by more than 20\% by delivering the linear model based ranking system. Reduced the score variance which might discourage players' passion at the beginning.
        \item[\textbf{+}] Determined and maintained suitable settings to ensure the normal daily operation of the AI in the production environment based on application data.
    \end{itemize}

    \item {\bf Data Analytics for a Chinese Fruit Retailing Giant} \hfill{\em May 2017 - November 2017}
    \begin{itemize}
    \setlength{\parskip}{0.2pt}
    \item[\textbf{+}] Generated daily reports including sales performance and forecast automatically with SQL and Python for shop managers to reduce more than 10\% of their repetitive workload.
    \item[\textbf{+}] Mitigated lose of potential sale opportunities and stock spoilage brought by incomplete human-made inventory strategies with statistical tools.
    \end{itemize}

\end{itemize}
\end{rSection}

\begin{rSection}{Conference Publication}
    Paper co-author of 2019 IJCAI(International Joint Conferences on Artificial Intelligence)
    \\ \textbf{DeltaDou: Expert-level Doudizhu AI through Self-play.}
\end{rSection}

\begin{rSection}{Technical Strengths}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{2ex}} l }
Modeling \& Analysis \ & Deep Learning, Reinforcement Learning, Statistical Learning \& Analysis \\
Software  \ \& Tools & Python, R, SQL, MongoDB, Git, Linux operations \\
\end{tabular}
\end{rSection}

\begin{rSection}{Nobel \& Leadership}
\begin{itemize}
\setlength{\itemindent}{-0.1in}
\setlength{\parskip}{0.2pt}
\item First Prize in the National Mathematics Competition for university students.
\item Second Prize in the National Contest of Mathematical Modeling of university students.
\item Team leader at Mathematics Summer Camp of the University of Science \& Technology of China.
\end{itemize}
\end{rSection}

\end{document}
